Assignment 3

### 2019-07-31 ex3/report/report.tex

To this end, we generated adversarial flows with the Carlini-Wagner method with $\ell_2$ distance and a tradeoff of 0.5. \autoref{adv_plots} depicts how the method manipulates flows for some exemplary attack categories.

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/1.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/2.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/3.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/4.pdf}
\caption{Successful manipulations performed by the Carlini-Wagner method.}
\label{adv_plots}
\end{figure*}

>>>>

To this end, we generated adversarial flows with the Carlini-Wagner method with $\ell_2$ distance and a tradeoff of 0.5. \autoref{adv_plots} depicts how the method manipulates flows for some exemplary attack categories. Depicted is the mean of both unmodified flows and adversarial flows  of samples of individual attack families considering both interarrival time and packet length.

The plots show that primarily features at the beginning of flows are modified. It is remarkable that it seems most promising to modifiy single packets while leaving most of the flow unchanged. In other cases, however, like depicted for the infiltration attack at the bottom, adversarial flows assume a complex pattern to circumvent detection.

\begin{figure*}[p]
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/1.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/2.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/3.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/4.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/5.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/6.pdf}
\caption{Successful manipulations performed by the Carlini-Wagner method.}
\label{adv_plots}
\end{figure*}
